Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-09-24 index.qmd
add updates

library(flextable)
library(tidyverse)
library(tidyterra)
# library(tidymodels)
library(Utilities.Package) 
library(patchwork)
library(sf) 
library(rnaturalearth) 
library(rnaturalearthdata) 
library(rnaturalearthhires)
library(ggforce) 
library(patchwork)
library(terra)
library(gt)
library(scales)
library(magick)
library(grid)
library(ggforce)
library(statebins)
library(ggridges)
library(ggspatial)
library(terrainr)
# library(ggpmisc)
library(broom)
library(stars)
library(gmodels)
library(caret)
library(rstudioapi)
library(terra)

@@

@@

total <- validation %>% 
  lazy_dt() %>% 
  group_by(res,true) %>% 
  dplyr::summarise(agreed = sum(same, na.rm = T),
          n_obs = n()) %>% 
  # ungroup() %>% 
  mutate(prop = agreed/n_obs) %>% 
  as_tibble() %>% 
  dplyr::filter(true != 1) %>% 
  mutate(true_fct = as.factor(true),
         area = res*res)

total %>% 
  ggplot(aes(x = res, y = prop, group = true, color = as.factor(true)))+
  geom_line()
  # scale_x_log10()

glm_res_true <- glm(prop ~ area * true_fct , data = total) 
glm_res <- glm(prop ~ area, data = total, family = "")

summary(glm_res)

Utilities.Package::Model_Check(glm_res)

NewData<-expand_grid(area=unique(total$area),
                    true_fct=unique(total$true_fct))

pred <- predict(glm_res_true, NewData, se.fit = T)

NewData <- NewData %>% 
  mutate(fit = pred$fit*100,
         se = pred$se.fit*100, 
         res = sqrt(area)/100)

  cols_fill <- c("1" = "#DAA520",
                 "2" = "#b3ff1a",
                 "3" = "#389318",
                 "4" = "#873e23",
                 "5" = "#b3002d",
                 "6" = "#70543e",
                 "7" = 'grey',
                 "8" = "#42c9bc")
plot <- ggplot(NewData)+
  geom_ribbon(aes(x = res, y = fit, ymax = fit+se, ymin = fit-se, 
                  color = true_fct, group = true_fct, fill = true_fct
                  ), alpha = 0.2)+
  geom_line(aes(x = res, y = fit,
                color = true_fct, group = true_fct
                ))+
  # ylim(0,1)+
      scale_fill_manual(name = NULL,
                        values = cols_fill,
                        labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water")) +
    scale_color_manual(name = NULL,
                      values = cols_fill,
                      labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water"))+
  theme_Bede()+
  xlab("Resolution (m)") +
  ylab("Agreement")+
  theme(axis.title = element_text(size = 20),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.key.size = unit(1, "cm"))

ggsave("Output/plot/resolution_plot.png", plot, bg = "white", height = 803*3, width = 1184*3, units = "px")

#### Area

test <-  validation %>% 
  lazy_dt() %>% 
  pivot_longer(c(true, pred), names_to = "source", values_to = "class") %>% 
  group_by(res,class,source) %>% 
  summarise(class_area = n()*(res*res)/(100*100)) %>% 
  as_tibble() %>% 
  pivot_wider(names_from = source, values_from = class_area) %>% 
  mutate(agreement = (1-abs(((pred-true)/(pred+true))))*100,
         # agreement1 = abs(pred-true)/max(pred,true)
         class = as.factor(class))

test %>%
  dplyr::filter(class != 1) %>%
  ggplot(aes(x = res, y =agreement))+
  geom_line(aes(color = class, group = class))

# test %>%
#   pivot_longer(c(pred,true), names_to = "dataset", values_to = "values") %>% 
#   dplyr::filter(class != 1) %>%
#     ggplot(aes(x = res, y = values, color = dataset, group = dataset))+
#   geom_line()+
#   facet_wrap(~ class, scales = "free")

glm_res_area <- glm(agreement ~ res * class , data = test)

summary(glm_res_area)

Utilities.Package::Model_Check(glm_res_area)

NewData<-expand_grid(res=unique(test$res),
                    class=unique(test$class))

pred <- predict(glm_res_area, NewData, se.fit = T)

NewData <- NewData %>% 
  mutate(fit = pred$fit,
         se = pred$se.fit)

NewData %>% 
  dplyr::filter(class != 1) %>% 
ggplot()+
  geom_ribbon(aes(x = res, y = fit, ymax = fit+se, ymin = fit-se, 
                  color = class, group = class, fill = class
                  ), alpha = 0.2)+
  geom_line(aes(x = res, y = fit,
                color = class, group = class
                ))+
  # ylim(0,1)+
      scale_fill_manual(name = NULL,
                        values = cols_fill,
                        labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water")) +
    scale_color_manual(name = NULL,
                      values = cols_fill,
                      labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water"))+
  theme_Bede()+
  xlab("Resolution (m)") +
  ylab("Agreement")+
  theme(axis.title = element_text(size = 20),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.key.size = unit(1, "cm"))

>>>>

library(flextable)
library(tidyverse)
library(tidyterra)
# library(tidymodels)
library(Utilities.Package) 
library(patchwork)
library(sf) 
library(rnaturalearth) 
library(rnaturalearthdata) 
library(rnaturalearthhires)
library(ggforce) 
library(patchwork)
library(terra)
library(gt)
library(scales)
library(magick)
library(grid)
library(ggforce)
library(statebins)
library(ggridges)
library(ggspatial)
library(terrainr)
# library(ggpmisc)
library(broom)
library(stars)
library(gmodels)
library(caret)
library(rstudioapi)
library(terra)
library(MapRs)

@@

if(file.exists("Data/Resampled_saved_data_total.csv")){

  total <- read.csv( "Data/Resampled_saved_data_total.csv")

@@

  total <- validation %>% 
  dtplyr::lazy_dt() %>% 
  group_by(res,true) %>% 
  dplyr::summarise(agreed = sum(same, na.rm = T),
          n_obs = n()) %>% 
  # ungroup() %>% 
  mutate(prop = agreed/n_obs) %>% 
  as_tibble() %>% 
  dplyr::filter(true != 1,
                true != 6,
                true != 7,
                true != 8) %>% 
  mutate(true_fct = as.factor(true),
         area = res*res)

  write.csv(total, "Data/Resampled_saved_data_total.csv", row.names = F)
}

# reframing <- total %>% 
#   group_by(true_fct) %>% 
#   dplyr::filter(res == 10) %>% 
#   ungroup() %>% 
#   mutate(diff = max(prop)-prop) %>% 
#   dplyr::select(true_fct,diff)
#   
# 
# total <- total %>% 
#   left_join(reframing, by = "true_fct") %>% 
#   mutate(prop = prop + diff) %>% 
#   dplyr::select(-diff)

total %>% 
  ggplot(aes(x = res, y = prop, group = true, color =true_fct))+
  geom_line()+
  theme_Bede_Map()

# glm_res_true <- glm(prop ~ area * true_fct , data = total, familly = mgcv::betar(link="logit")) 
glm_res_true <- mgcv::gam(prop ~ area * true_fct , data = total, familly = mgcv::betar(link="logit"))

summary(glm_res_true)

Utilities.Package::Model_Check(glm_res_true)

NewData<-expand_grid(res=unique(total$res),
                    true_fct=unique(total$true_fct),
                    area = res*res)

pred <- predict(glm_res_true, NewData, se.fit = T, type = "link")

NewData <- NewData %>% 
  mutate(fit = pred$fit*100,
         se = pred$se.fit*100,
         true_fct=as.factor(true_fct))

  cols_fill <- c("1" = "#DAA520",
                 "2" = "#b3ff1a",
                 "3" = "#389318",
                 "4" = "#873e23",
                 "5" = "#b3002d",
                 "6" = "#70543e",
                 "7" = 'grey',
                 "8" = "#42c9bc")

(plot <- ggplot(NewData)+
  geom_ribbon(aes(x = sqrt(area), y = fit, ymax = fit+se, ymin = fit-se, 
                  color = true_fct, group = true_fct, fill = true_fct
                  ), alpha = 0.2)+
  geom_line(aes(x = sqrt(area), y = fit,
                color = true_fct, group = true_fct
                ))+
  # ylim(0,1)+
      scale_fill_manual(name = NULL,
                        values = cols_fill,
                        labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water")) +
    scale_color_manual(name = NULL,
                      values = cols_fill,
                      labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water"))+
  theme_Bede()+
  xlab("Resolution (m)") +
  ylab("Agreement")+
  theme(axis.title = element_text(size = 20),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.key.size = unit(1, "cm"))

    # scale_x_log10()

  )

ggsave("Output/plot/resolution_plot.png", plot, bg = "white", height = 803*3, width = 1184*3, units = "px")
```
